---
title: "P1-shepherd"
author: "Avery Shepherd"
date: "8/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(corrplot)
library(RColorBrewer)
```

```{r}
green = read_csv("greenbuildings.csv")
green_occ = green %>% filter(leasing_rate > 10)


green_sqft = green_occ %>% filter(green_rating == 1) %>% summarise(rentsqft = mean(Rent))
green_sqft = green_sqft[[1, 1]]
cat('green rent per sqft is', green_sqft)
non_green_sqft = green_occ %>% filter(green_rating == 0) %>% summarise(rentsqft = mean(Rent))
non_green_sqft = non_green_sqft[[1, 1]]
cat('\nnon green rent per sqft is', non_green_sqft)

sqfts = data.frame(c(green_sqft, non_green_sqft))
```
The intern says that green buildings cost 27.60 per sqft when the actual cost is 30.03 so there is a 2.43 dollar discrepancy. The intern also says non green buildings cost 25 per sqft when they actually cost 28.58 so there is a 3.58 discrepancy.

```{r}
cat('the actual difference for the building if it were green is this dollar amount: \n')
250000*(green_sqft-non_green_sqft)
```
That is $288337 less than predicted.

If costs of the building are an extra 5 million to make it green it would actually take this many years to pay off the extra building costs:
```{r}
5000000/361663
```
Which is over 6 years longer than the analyst projected. 
After almost 14 years you would then be making $361663 a year extra over having a green building.

```{r}
# corrplot(c)

corrplot(cor(green_occ), col=brewer.pal(n=8, name="RdYlBu"), type = "upper")
```
cluster rent (the buildings location) has a high impact on Rent
electricity cost has high impact on rent

```{r}
ggplot(data = green_occ, aes(x = cluster_rent, y = Rent)) + geom_point()
ggplot(data = green_occ, aes(x = as.factor(green_rating), y = cluster_rent)) + geom_boxplot()
```
As you increase cluster, rent increases. cluster does not impact green rating. 
```{r}
ggplot(data = green_occ, aes(x = Electricity_Costs, y = Rent)) + geom_point()
ggplot(data = green_occ, aes(x = as.factor(green_rating), y = Electricity_Costs)) + geom_boxplot()
```
Higher electricity costs are generally associated with higher rent

##Portfolio Management

```{r}
library(mosaic)
library(quantmod)
library(foreach)

```

```{r}

##First portfolio - diversified industries including energy, financial, construction, and transportation
mystocks = c("ITB", "OIH", "IYT", "KRE")
getSymbols(mystocks, from = "2016-01-01")

# Adjust for splits and dividends
ITBa = adjustOHLC(ITB)
OIHa = adjustOHLC(OIH)
IYTa = adjustOHLC(IYT)
KREa = adjustOHLC(KRE)

```

```{r}
#Portfolio 1 - Randomly selected 5 ETFs in Asia Pacific

all_returns = cbind(ClCl(ITBa),ClCl(OIHa),ClCl(IYTa),ClCl(KREa))
head(all_returns)
# first row is NA because we didn't have a "before" in our data
all_returns = as.matrix(na.omit(all_returns))

```


```{r}
initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
	total_wealth = initial_wealth
	weights = c(0.25, 0.25, 0.25, 0.25)
	holdings = weights * total_wealth
	n_days = 20
	wealthtracker = rep(0, n_days)
	for(today in 1:n_days) {
		return.today = resample(all_returns, 1, orig.ids=FALSE)
		holdings = holdings + holdings*return.today
		total_wealth = sum(holdings)
		holdings = weights * total_wealth
		wealthtracker[today] = total_wealth
	}
	wealthtracker
}
```

```{r}
total_wealth = sum(holdings)
total_wealth
```
```{r}
P1 = quantile(sim1[,n_days]- initial_wealth, prob=0.05)
P1
```

```{r}
##Second portfolio - Health & Biotech ETFs with highest percentage increase based on YTD. This is considered an aggressive portfolio

mystocks = c("BBH", "HELX", "CHNA", "IDNA", "RYH")
getSymbols(mystocks, from = "2016-01-01")

# Adjust for splits and dividends
BBHa = adjustOHLC(BBH)
HELXa = adjustOHLC(HELX)
CHNAa = adjustOHLC(CHNA)
IDNAa = adjustOHLC(IDNA)
RYHa = adjustOHLC(RYH)
```
```{r}
all_returns = cbind(ClCl(BBHa),ClCl(HELXa),ClCl(CHNAa),ClCl(IDNAa),ClCl(RYHa))
head(all_returns)
# first row is NA because we didn't have a "before" in our data
all_returns = as.matrix(na.omit(all_returns))
```

```{r}
initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
	total_wealth = initial_wealth
	weights = c(0.2, 0.2, 0.2, 0.2, 0.2)
	holdings = weights * total_wealth
	n_days = 20
	wealthtracker = rep(0, n_days)
	for(today in 1:n_days) {
		return.today = resample(all_returns, 1, orig.ids=FALSE)
		holdings = holdings + holdings*return.today
		total_wealth = sum(holdings)
		holdings = weights * total_wealth
		wealthtracker[today] = total_wealth
	}
	wealthtracker
}

wealthtracker
```

```{r}
total_wealth = sum(holdings)
total_wealth
```
```{r}
P2 = quantile(sim1[,n_days]- initial_wealth, prob=0.05)
P2
```

```{r}
##Third portfolio - Mix of mid and large cap growth ETFs

mystocks = c("XMMO", "SCHM", "SFYX", "VTI", "ITOT", "SCHG", "GSLC", "MDYG", "IVOG", "DIA")
getSymbols(mystocks, from = "2016-01-01")

# Adjust for splits and dividends

XMMOa = adjustOHLC(XMMO)
SCHMa = adjustOHLC(SCHM)
SFYXa = adjustOHLC(SFYX)
VTIa = adjustOHLC(VTI)
ITOTa = adjustOHLC(ITOT)
SCHGa = adjustOHLC(SCHG)
GSLCa = adjustOHLC(GSLC)
MDYGa = adjustOHLC(MDYG)
IVOGa = adjustOHLC(IVOG)
DIAa = adjustOHLC(DIA)

```

```{r}
all_returns = cbind(ClCl(XMMOa),ClCl(SCHMa),ClCl(SFYXa),ClCl(VTIa),ClCl(ITOTa),ClCl(SCHGa),ClCl(GSLCa),ClCl(MDYGa),ClCl(IVOGa),ClCl(DIAa))
head(all_returns)
# first row is NA because we didn't have a "before" in our data
all_returns = as.matrix(na.omit(all_returns))
```

```{r}
initial_wealth = 100000
sim1 = foreach(i=1:5000, .combine='rbind') %do% {
	total_wealth = initial_wealth
	weights = c(0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1, 0.1)
	holdings = weights * total_wealth
	n_days = 20
	wealthtracker = rep(0, n_days)
	for(today in 1:n_days) {
		return.today = resample(all_returns, 1, orig.ids=FALSE)
		holdings = holdings + holdings*return.today
		total_wealth = sum(holdings)
		holdings = weights * total_wealth
		wealthtracker[today] = total_wealth
	}
	wealthtracker
}

wealthtracker
```

```{r}
total_wealth = sum(holdings)
total_wealth
```
```{r}
P3 = quantile(sim1[,n_days]- initial_wealth, prob=0.05)
P3
```


```{r}
cat("Portfolio 1 value at risk 5%: ", abs(P1), "\n")
cat("Portfolio 2 value at risk 5%: ", abs(P2), "\n")
cat("Portfolio 3 value at risk 5%: ", abs(P3))
```

I tried to pick a few different types of portfolios to see the change in VaR. The first portfolio includes ETfs from 4 different industries including transportation, construction, financial, and energy. This diverse portfolio returned the highest 5% value at risk with an expected loss of ~14%. Portfolio 2 was the most aggressive portfolio with Health & Biotech ETFs that had the highest percentage increase YTD. This portfolio had the lowest 5% VaR with an expected loss of about ~9.5%. The third portfolio included a mix of large and mid cap growth ETFs and returned an expected loss of ~10.5% for the 5% VaR.

Based on these VaR results, we can assume having a very diverse portfolio leads to more risk and having a portfolio with high growth ETFs will minimize risk. Of course, we would have to try out many other portfolios to fully understand high and low risk portfolios. 