---
title: "P1-shepherd"
author: "Avery Shepherd"
date: "8/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(corrplot)
library(RColorBrewer)
```

```{r}
green = read_csv("greenbuildings.csv")
green_occ = green %>% filter(leasing_rate > 10)


green_sqft = green_occ %>% filter(green_rating == 1) %>% summarise(rentsqft = mean(Rent))
green_sqft = green_sqft[[1, 1]]
cat('green rent per sqft is', green_sqft)
non_green_sqft = green_occ %>% filter(green_rating == 0) %>% summarise(rentsqft = mean(Rent))
non_green_sqft = non_green_sqft[[1, 1]]
cat('\nnon green rent per sqft is', non_green_sqft)

sqfts = data.frame(c(green_sqft, non_green_sqft))
```
The intern says that green buildings cost 27.60 per sqft when the actual cost is 30.03 so there is a 2.43 dollar discrepancy. The intern also says non green buildings cost 25 per sqft when they actually cost 28.58 so there is a 3.58 discrepancy.

```{r}
cat('the actual difference for the building if it were green is this dollar amount: \n')
250000*(green_sqft-non_green_sqft)
```
That is $288337 less than predicted.

If costs of the building are an extra 5 million to make it green it would actually take this many years to pay off the extra building costs:
```{r}
5000000/361663
```
Which is over 6 years longer than the analyst projected. 
After almost 14 years you would then be making $361663 a year extra over having a green building.

```{r}
# corrplot(c)

corrplot(cor(green_occ), col=brewer.pal(n=8, name="RdYlBu"), type = "upper")
```
cluster rent (the buildings location) has a high impact on Rent
electricity cost has high impact on rent






